Artin Group Presentations Arising from Cluster Algebras

### 2014-07-30 Paper.tex

A \textit{cluster algebra} is an integral domain which can be generated by a set of elements called \textit{cluster variables} that satisfy certain exchange relations. Following the style of \cite{FZ02} and \cite{BM13}, we will define cluster algebras in terms of \textit{skew-symmetrisable} matrices (that is, a matrix $B$ such that there exists a diagonal matrix $D$ of the same size with $D_{ii} >0$ such that $DB$ is skew-symmetric). Let $\mathbb{F} = \mathbb{Q}(u_1, u_2, \ldots, u_n)$ be the field of rational functions in $n$ indeterminates over $\mathbb{Q}$. We will define an \textit{intial seed} for the cluster algebra to be a fixed pair $(\textbf{x}, B)$, where $\textbf{x} = \{x_1, \ldots, x_n\}$ is a free generating set of $\mathbb{F}$ and $B$ is an $n \times n$ skew-symmetric matrix. Define $x_k^{\prime} \in \mathbb{F}$ by the \textit{exchange relation}
\begin{displaymath}
x_k^{\prime}x_k = \prod_{B_{ik} > 0}{x_i^{B_{ik}}} + \prod_{B_{ik} < 0}{x_i^{-B_{ik}}}
\end{displaymath}
Then, given an initial seed $(\textbf{x}, B)$ and $k \in {1,2,\ldots,n}$, we can define a \textit{mutation} of the seed at $k$, denoted $\mu_k(\boldsymbol{x}, B) = (\textbf{x}^{\prime}, B^{\prime})$ where:
\begin{displaymath}
B_{ij}^{\prime} = \begin{cases} - B_{ij} & \mbox{ if } i = k \mbox{ or } j = k;\\
																B_{ij} + \frac{|B_{ik}|B_{kj} + B_{ik}|B_{kj}|}{2} & \mbox{ otherwise. }\\
									\end{cases}
\end{displaymath}
and $\textbf{x}^{\prime} = { x_1, x_2, \ldots, x_{k-1}, x_k^{\prime}, x_{k+1}, \ldots, x_n}$. 
Such a mutation or a sequence of such mutations generate \textit{seeds} which in turn generate all cluster variables in that, for each $\textbf{x} = { x_1, \ldots, x_n}$ corresponding to a seed of the cluster algebra, the entries $x_i$ are the cluster variables. \\

 A cluster algebra is said to be of \textit{finite type} if the number of cluster variables that generate it is finite (if it has finitely many seeds). For each finite type cluster algebra, we can associate to its corresponding skew-symmetrisable matrix an edge-weighted, oriented graph, called a \textit{diagram}. We will often denote this diagram by $\Gamma$, and the vertex set of $\Gamma$ by $\V$. We will denote two connected vertices by $i \rightarrow j$, or by $i\--\ j$ if the orientation is not specified. The diagram is determined by, for $i, j \in \V$, $i \xrightarrow{w} j$ if and only if $B_{ij} > 0$ and $w = |B_{ij}B_{ji}|$ is the weight of the edge. A skew-symmetrisable matrix $B$ is \textit{2-finite} if $|B_{ij}B_{ji}| \leq 3$ for $i, j \in { 1, \ldots, n }$.  By \cite[7.5]{FZ02}, we have that if $B$ is 2-finite, all 3-cycles in the unoriented graph underlying our diagram must be oriented cyclically. \\

@@

    \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
  {
    & |[name = ul]|\circ& |[name = ur]|\bullet\\
    %
    &|[name=dl]| \circ &|[name=dr]| \circ \\
  };
\draw[->]
  (ul) to node[above] {1} (ur)
  ;
  \draw[->]
  (dl) to node[left]{2}(ul)
  ;
  \draw[->]
  (dr) to node[below]{1}(dl)
  ;
  \draw[->]
  (ur) to node[right]{2} (dr)
  ;
    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){1};
   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){k=2};
    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};

@@

\end{note}
\begin{defn}
\cite[Beginning of section 1.2]{artin} \todo{put reference for artin, found at the bottom, in bibliography, but I don't know how to use this bibliography format.}
For $M \in M_{n \times n}(\mathbb Z \cup \infty)$ a matrix whose entries can take values in the real numbers or infinity, satisfying $M_{i,j} = M_{j,i}$ we define the associated {\it Artin group} in terms of generators and relations by
\begin{align*}
	A = \langle x_1,\ldots, x_n| \langle x_i,x_j \rangle^{M_{i,j}}\forall i,j \text{ with } m_{i,j}<\infty \rangle,
\end{align*}
\end{defn}

@@

\begin{proof}
For case $(a)$, suppose without loss of generality that $i=k$.  Note that $m_{ij}^\prime = m_{ij}$. The only nontrivial case is when there is an arrow $j\rightarrow k =i$.  Since $i$ and $j$ are connected in this case, $m_{ij}$ is one of 3, 4, or 6.

>>>>

A \textit{cluster algebra} is an integral domain which can be generated by a set of elements called \textit{cluster variables} that satisfy certain exchange relations. Following the style of \cite{FZ02} and \cite{BM13}, we will define cluster algebras in terms of \textit{skew-symmetrisable} matrices (that is, a matrix $B$ such that there exists a diagonal matrix $D$ of the same size with $D_{ii} >0$ such that $DB$ is skew-symmetric). Let $\mathbb{F} = \mathbb{Q}(u_1, u_2, \ldots, u_n)$ be the field of rational functions in $n$ indeterminates over $\mathbb{Q}$. We will define an \textit{intial seed} for the cluster algebra to be a fixed pair $(\textbf{x}, B)$, where $\textbf{x} = \{x_1, \ldots, x_n\}$ is a free generating set of $\mathbb{F}$ and $B$ is an $n \times n$ skew-symmetric matrix. Define $x_k^{\prime} \in \mathbb{F}$ by the \textit{exchange relation}
\begin{displaymath}
x_k^{\prime}x_k = \prod_{B_{ik} > 0}{x_i^{B_{ik}}} + \prod_{B_{ik} < 0}{x_i^{-B_{ik}}}
\end{displaymath}
Then, given an initial seed $(\textbf{x}, B)$ and $k \in {1,2,\ldots,n}$, we can define a \textit{mutation} of the seed at $k$, denoted $\mu_k(\boldsymbol{x}, B) = (\textbf{x}^{\prime}, B^{\prime})$ where:
\begin{displaymath}
B_{ij}^{\prime} = \begin{cases} - B_{ij} & \mbox{ if } i = k \mbox{ or } j = k;\\
B_{ij} + \frac{|B_{ik}|B_{kj} + B_{ik}|B_{kj}|}{2} & \mbox{ otherwise. }\\
\end{cases}
\end{displaymath}

and $\textbf{x}^{\prime} = \left\{ x_1, x_2, \ldots, x_{k-1}, x_k^{\prime}, x_{k+1}, \ldots, x_n \right\}$.
Such a mutation or a sequence of such mutations generate \textit{seeds} which in turn generate all cluster variables in that, for each $\textbf{x} = \left\{ x_1, \ldots, x_n \right\}$ corresponding to a seed of the cluster algebra, the entries $x_i$ are the cluster variables. \\

 A cluster algebra is said to be of \textit{finite type} if the number of cluster variables that generate it is finite (if it has finitely many seeds). For each finite type cluster algebra, we can associate to its corresponding skew-symmetrisable matrix an edge-weighted, oriented graph, called a \textit{diagram}. We will often denote this diagram by $\Gamma$, and the vertex set of $\Gamma$ by $\V$. We will denote two connected vertices by $i \rightarrow j$, or by $i\--\ j$ if the orientation is not specified. The diagram is determined by, for $i, j \in \V$, $i \xrightarrow{w} j$ if and only if $B_{ij} > 0$ and $w = |B_{ij}B_{ji}|$ is the weight of the edge. A skew-symmetrisable matrix $B$ is \textit{2-finite} if $|B_{ij}B_{ji}| \leq 3$ for $i, j \in \left\{ 1, \ldots, n \right\}$. By \cite[7.5]{FZ02}, we have that if $B$ is 2-finite, all 3-cycles in the unoriented graph underlying our diagram must be oriented cyclically. \\

@@

    \matrix[matrix of math nodes,column sep={40pt,between origins},row
    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
  {
    & |[name = ul]|\circ& |[name = ur]|\bullet\\
    %
    &|[name=dl]| \circ &|[name=dr]| \circ \\
  };
\draw[->]
  (ul) to node[above] {1} (ur)
  ;
  \draw[->]
  (dl) to node[left]{2}(ul)
  ;
  \draw[->]
  (dr) to node[below]{1}(dl)
  ;
  \draw[->]
  (ur) to node[right]{2} (dr)
  ;

    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){1};
   \node [yshift = .4 cm,xshift = .4 cm] at (ur){k=2};
    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};

@@

\end{note}
\begin{defn}
\cite[Beginning of section 1.2]{artin} \todo{put reference for artin, found at the bottom, in bibliography, but I don't know how to use this bibliography format. - it's just BibTex, which you'll almost certainly want to learn at some point.  Try editing References.bib, and if you have trouble feel free to ask me for help - David}
For $M \in M_{n \times n}(\mathbb Z \cup \infty)$ a matrix whose entries can take values in the real numbers or infinity, satisfying $M_{i,j} = M_{j,i}$ we define the associated {\it Artin group} in terms of generators and relations by
\begin{align*}
A = \langle x_1,\ldots, x_n| \langle x_i,x_j \rangle^{M_{i,j}}\forall i,j \text{ with } m_{i,j}<\infty \rangle,
\end{align*}
\end{defn}

@@

\begin{proof}
For case $(a)$, suppose without loss of generality that $i=k$.  Note that $m_{ij}^\prime = m_{ij}$. The only nontrivial case is when there is an arrow $j\rightarrow k = i$.  Since $i$ and $j$ are connected in this case, $m_{ij}$ is one of 3, 4, or 6.
